2nd_draft

### 2020-03-19 src/2nd_draft.Rmd
assign
assign more

Before any prediction on the future mill rate of Metro Vancouver’s real estate market was made, exploratory data analysis was performed to explore and visualize the main characteristics of our dataset and found relationships between Mill Rate vs. Assessment, Mill Rate vs. Land Total, Mill Rate vs. Improvement Total and Mill Rate vs. Number of Properties were performed. From our initial analysis, outliers in municipalities had been found. Data transformation - calculating the average total assessment, was used to reduce the effect of outliers.

@@

### Measure of goodness of fit and prediction power

@@

We build the three models using all features and compare their goodness of fit, and then will examine their prediction power on testing data.

@@

@@

@@

write.csv(assessment_2020.final, "../Data/Assessment/assessment_2020.final")
write.csv(b, "../Data/assessment_2020.csv")
```

###Linear Model

>>>>

Before any prediction on the future mill rate of Metro Vancouver’s real estate market was made, exploratory data analysis was performed to explore and visualize the main characteristics of our dataset and found relationships between Mill Rate vs. Assessment, Mill Rate vs. Land Total, and Mill Rate vs. Improvement Total were performed. From our initial analysis, outliers in municipalities had been found. Data transformation - calculating the average total assessment, was used to reduce the effect of outliers.

@@

## TODO modify this part based on the comment in the following link (Leonie)
## _______________________________
https://github.com/STAT450-550/RealEstate/blob/450/doc/Peter_Han_Individual_edit.pdf
### Measure of goodness of fit and prediction power

@@

We build the three models using all features and compare their goodness of fit, and then will examine their prediction power on testing data.
##_____________________________________________

@@

assessment_transform %>%
                   ggplot(aes(x=assessTotal,
                              y=rate,group=AddressAssessorMunicipalityDesc,
                              color=AddressAssessorMunicipalityDesc)) + 
                   geom_point() + 
                   ggtitle(sprintf("mill rate vs total assessment value")) + 
                   geom_smooth(aes(group = 1), size = 0.5, method = "lm", se = FALSE, colour = "black")

assessment_transform %>%
                   ggplot(aes(x=landTotal,
                              y=rate,group=AddressAssessorMunicipalityDesc,
                              color=AddressAssessorMunicipalityDesc)) + 
                   geom_point() + 
                   ggtitle(sprintf("mill rate vs total land assessment value")) + 
                   geom_smooth(aes(group = 1), size = 0.5, method = "lm", se = FALSE, colour = "black")
assessment_transform %>%
                   ggplot(aes(x=improvementTotal,
                              y=rate,group=AddressAssessorMunicipalityDesc,
                              color=AddressAssessorMunicipalityDesc)) + 
                   geom_point() + 
                   ggtitle(sprintf("mill rate vs total improvement assessment value")) + 
                   geom_smooth(aes(group = 1), size = 0.5, method = "lm", se = FALSE, colour = "black")

@@

## ___________________________
## TODO KW result table, explanation of all plots (Yuting)
## ___________________________

##_____________________________
## TODO modify this part using boxplot and tables, change desrciptions (Leonie)
###Linear Model

@@

write.csv(assessment_2020.final, "../Data/Assessment/assessment_2020.final")
write.csv(b, "../Data/assessment_2020.csv")
```
##_______________________________________
